The Socialization of Meritocracy: The role of the Family and the School

### 2023-06-16 docs/presentacion-effort/presentation-effort.Rmd
ajustes slides

----
<br>
.espaciosimplelineas[
.small[
Julio Iturra -  Bremen Int. Graduate School of Social Sciences
<br>
Juan Carlos Castillo -  Universidad de Chile
<br>
Francisco Meneses & Martín Venegas
] 
]

@@

- Highschool students (2nd) and parents (n = 541) nested in schools (n = 60)

@@

.bold[Obtained:] _What was your last year average grade? If you don't remember exactly, please give an approximate grade._

.bold[Deserved:] _And, what grade average do you think you deserved?_ 
$$\text{Justice}= \ln\biggl(\frac{\text{grade obtained}}{\text{grade deserved}}\biggl)$$

@@

_Taking into account the time I ddedicate to my studies, the grades I get are:_

.center[![:scale 90%](images/direct.png)]
  ]

@@

---
class: roja middle

# ¡Thank you!

@@

@@

----
<br>
.espaciosimplelineas[
.medium[
Julio Iturra -  Bremen Int. Graduate School of Social Sciences
<br>
Juan Carlos Castillo -  Universidad de Chile
<br>
Francisco Meneses & Martín Venegas
] 
]

>>>>

----
<br>
.espaciosimplelineas[
.small[
Julio Iturra -  Bremen Int. Graduate School of Social Sciences
[jiturra@bigsss.uni-bremen.de](jiturra@bigsss.uni-bremen.de)
<br>
Juan Carlos Castillo -  Universidad de Chile
<br>
Francisco Meneses & Martín Venegas
] 
]

@@

- High school students (2nd) and parents (n = 541) nested in schools (n = 60)

@@

.pull-left[
.bold[Obtained:] _What was your last year average grade? If you don't remember exactly, please give an approximate grade._ (M= 5.8)

.bold[Deserved:] _And, what grade average do you think you deserved?_ (M=6.0)

Min: 1 / Max: 7

$$\text{Justice}= \ln\biggl(\frac{\text{grade obtained}}{\text{grade deserved}}\biggl)$$

@@

_Taking into account the time I dedicate to my studies, the grades I get are:_

.center[![:scale 90%](images/direct.png)]

@@

---
class: roja middle center

# Thank you!

@@

[jiturra@bigsss.uni-bremen.de](jiturra@bigsss.uni-bremen.de)

[github.com/juancarloscastillo/socialisacion-merit](https://github.com/juancarloscastillo/socialisacion-merit)

@@

----
<br>
.espaciosimplelineas[
.medium[
Julio Iturra -  Bremen Int. Graduate School of Social Sciences
[jiturra@bigsss.uni-bremen.de](jiturra@bigsss.uni-bremen.de)
<br>
Juan Carlos Castillo -  Universidad de Chile
<br>
Francisco Meneses & Martín Venegas
] 
]
